Supplement 7

### 2023-12-18 Code/Supplement 1B_figures.Rmd
removed some commented out code
added rt data, updated figures

############################################################################
############################################################################

@@

####
load(here("Data/cases_county_forecasts_2022-04-04.Rdata"))
size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

>>>>

@@

####
load(here("Data/cases_county_forecasts.Rdata"))
size <-read.csv(here("Data/SVI2018_US_COUNTY.csv")) %>%
  dplyr::select(FIPS, E_TOTPOP) %>%
  rename(location=FIPS) %>%
  mutate(location=as.character(location),
         location=ifelse(nchar(location)==4, paste0("0", location), location),
         pop_size_quant2=cut(E_TOTPOP, breaks = quantile(E_TOTPOP, probs = seq(0, 1, 0.20)),
                             include.lowest = TRUE, labels = 1:5)
  ) %>% 
  dplyr::select(-E_TOTPOP) 
all_dat <-all_dat %>% left_join(., size, by="location") 
rm(size)
counts <-all_dat %>%
  filter(!(model %in% sec_models),
         sub_date >= start_date & sub_date <= stop_date) %>%
  filter(type=="point")

### 2023-12-18 Code/Supplement 2_Outliers.Rmd
removed some commented out code
added rt data, updated figures

## rename locations based on state names
states <-read.csv(here("Data/locations.csv")) %>%
  rename(fips = location) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  dplyr::select(abbreviation, location_name)

@@

  #Phases
  marg_means[[i]] <-ggemmeans(model_rev[[i]], terms=c("phase")) %>% #, "cases_log_std[-2:2]")) %>%
    rename(phase=x,
           cases=group) %>%

>>>>

## rename locations based on state names
states <-tidycensus::fips_codes %>% 
  rename(fips = state_code, 
         abbreviation=state, 
         location_name=state_name) %>%
  mutate(fips = as.character(fips)) %>%
  filter(nchar(fips)==2) %>%
  distinct() %>%
  dplyr::select(abbreviation, location_name)

@@

  #Phases
  marg_means[[i]] <-as.data.frame(ggemmeans(model_rev[[i]], terms=c("phase")) %>% 
    rename(phase=x,
           cases=group))

  marg_means[[i]] <-marg_means[[i]] %>%

### 2023-12-18 Code/Supplement 3.1_figure.rmd
added rt data, updated figures

cov.95 <-function() {
  load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

  load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

load(here("Data/cases_non large counties_forecasts_for analysis_2022-08-18.rdata"))
subs_co_other <-submissions(df=dat_other_count) %>%
  rename_counts()

>>>>

cov.95 <-function() {
  load(here("Data/cases_large counties_forecasts_for analysis.rdata"))

@@

  load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))

@@

load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
subs_co <-submissions(df=dat_large_count) %>%
  mutate(pop_size_quant2="County Forecasts: Size Quantile 5")

load(here("Data/cases_non large counties_forecasts_for analysis.rdata"))
subs_co_other <-submissions(df=dat_other_count) %>%
  rename_counts()

### 2023-12-18 Code/Supplement 6_all figures.Rmd
added rt data, updated figures

---
title: "Supplement 5"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

@@

### Supplement 5: Horizon specific plots

@@

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))

@@

# Largest Counties
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

```{r Fig S5.1, echo=FALSE, warning=F, message=F, fig.height=12, fig.width=12}

@@

load(here("Data/cases_nat_state_forecasts_for analysis_2022-08-18.rdata"))
load(here("Data/cases_large counties_forecasts_for analysis_2022-08-18.rdata"))

@@

```{r Fig S5.2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}

@@

```{r Fig S5.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}

>>>>

---
title: "Supplement 6"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

@@

### Supplement 6: Horizon specific plots

@@

load(here("Data/cases_nat_state_forecasts_for analysis.rdata"))

@@

# Largest Counties
load(here("Data/cases_large counties_forecasts_for analysis.rdata"))
coverage_count <-cov.fig_dat(filter(dat_large_count, sub_date <= cut_date,
                                   !grepl("2", target),
                                   !grepl("3", target)))
labels_count <-data_labels(coverage_count) 
Cov.Co <-cov.plot(coverage_count, labels_count) +
  facet_wrap(~target) +
  theme(strip.text=strip.text_standard, strip.background=strip.background_standard) +
  labs(title="C. Coverage for Large County Forecasts*",
       x="Expected Coverage")

@@

```{r Fig S6.1, echo=FALSE, warning=F, message=F, fig.height=12, fig.width=12}

@@

load(here("Data/cases_nat_state_forecasts_for analysis.rdata"))
load(here("Data/cases_large counties_forecasts_for analysis.rdata"))

@@

```{r Fig S6.2, echo=FALSE, warning=FALSE, message=FALSE, fig.height=11, fig.width=12}

@@

```{r Fig S6.3, echo=FALSE, warning=FALSE, message=FALSE, fig.height=10, fig.width=15}

### 2023-12-18 Code/Supplement 7_figures.Rmd
added rt data, updated figures

---
title: "Supplement 6"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

@@

### Supplement 6

@@

  marg_means[[i]] <-ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
    rename(phase=x,
           cases=group) %>% 
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           cases=as.numeric(as.character(cases)),
           cases_log_back=(cases*means_sds[[i]]$sd_log_cases) + means_sds[[i]]$mean_log_cases) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up),
           cases_back_rescale=exp(cases_log_back))
}
marg_means <-do.call(rbind.data.frame, marg_means)

@@

# Figure
FigS6 <-marg_means %>%
  ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
  geom_line(aes(color=phase)) +
  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase), alpha=0.35) +
  scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  scale_color_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  labs( y="Marginal Mean \nWeighted Interval Score", x="Reported cases") +
  facet_wrap(~model) +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard,
        legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.x = element_text(angle = 45, hjust=1)) +
  guides(fill=guide_legend(nrow=2, byrow=TRUE))

@@

```{r Fig s6, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=11.5}

grid.draw(shift_legend(FigS6))

>>>>

---
title: "Supplement 7"
author: "VKL"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    keep_md: yes
---

@@

### Supplement 7

@@

  marg_means[[i]] <-as.data.frame(ggemmeans(model[[i]], terms=c("phase", "cases_log_std[-1.96:1.96]")) %>%
    rename(phase=x,
           cases=group))

  marg_means[[i]] <-marg_means[[i]] %>% 
    mutate(model=team[i],
           predicted_back=(predicted*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_lo=(conf.low*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           predicted_back_up=(conf.high*means_sds[[i]]$sd_log_WIS) + means_sds[[i]]$mean_log_WIS,
           cases=as.numeric(as.character(cases)),
           cases_log_back=(cases*means_sds[[i]]$sd_log_cases) + means_sds[[i]]$mean_log_cases) %>%
    mutate(predicted_back_rescale=exp(predicted_back),
           predicted_back_lo_rescale=exp(predicted_back_lo),
           predicted_back_up_rescale=exp(predicted_back_up),
           cases_back_rescale=exp(cases_log_back))
}
marg_means <-do.call(rbind.data.frame, marg_means)

@@

# Figure
FigS7 <-marg_means %>%
  ggplot(., aes(cases_back_rescale, predicted_back_rescale)) +
  geom_line(aes(color=phase)) +
  geom_ribbon(aes(ymin=predicted_back_lo_rescale, ymax=predicted_back_up_rescale, fill=phase), alpha=0.35) +
  scale_fill_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  scale_color_manual(breaks = c("Increasing", "Decreasing", "Unclassified", "Peak", "Nadir"), 
                      values=c("#fdae61", "#abdda4", "#bababa", "#d7191c", "#2b83ba")) +
  labs( y="Marginal Mean \nWeighted Interval Score", x="Reported cases") +
  facet_wrap(~model) +
  theme_bw() +
  theme(axis.title.y=axis.title.y_standard,
        legend.title = element_blank(), legend.text=legend.text_standard,
        strip.text=strip.text_standard, strip.background=strip.background_standard,
        axis.text.x = element_text(angle = 45, hjust=1)) +
  guides(fill=guide_legend(nrow=2, byrow=TRUE))

@@

```{r Fig S7, echo=FALSE, warning=F, message=F, fig.height=8, fig.width=11.5}

grid.draw(shift_legend(FigS7))
